\ProjectName{}: Data Imputation as a Query Optimization

### 2016-12-12 paper/relatedwork.tex
Add reference to data cleaning survey paper

\subsection{Missing Values and Statistics}
Imputation of missing values is a widely studied field within the statistics and machine
learning communities. As highlighted in \cite{gelman2006data}, missing data
can appear for a variety of reasons, including both random and conditioned on
existing values (observed and missing). Methods in the statistical community
focus on correctly modeling relationships between the attributes to factor in
varied forms of missingness.

Burgette and Reiter (\cite{burgette2010multiple}) discuss the usage of
sequential regression trees for imputing missing data.

@@

>>>>

\subsection{Missing Values and Statistics}

Imputation of missing values is a widely studied field within the statistics and machine
learning communities. As highlighted in \cite{gelman2006data}, missing data
can appear for a variety of reasons, including both random and conditioned on
existing values (observed and missing). Methods in the statistical community
focus on correctly modeling relationships between the attributes to factor in
varied forms of missingness. For example, Burgette and Reiter
(\cite{burgette2010multiple}) discuss the usage of sequential regression trees
for imputing missing data.

@@

Database system developers and others have worked on techniques to automatically
detect dirty values, whether missing or otherwise, and rectify the errors is
possible. A survey of methods and systems is provided in
\cite{hellerstein2008quantitative}.
